Abstractions for Type-Level Programming

### 2022-04-23 ack.tex
Revert "Remove diff"
This reverts commit baca8b24302dc02b00fcc2f8fee3e4173838d1a4.

I would also like to thank the other members of my thesis committee, Paolo Giarrusso, Richard Eisenberg, and Viktor Kuncak, for reviewing my dissertation and for providing valuable feedback.

>>>>

\begin{diff}
I would also like to thank the other members of my thesis committee, Paolo Giarrusso, Richard Eisenberg, and Viktor Kuncak, for reviewing my dissertation and for providing valuable feedback.
\end{diff}

### 2022-04-23 thesis.tex
Revert "Remove diff"
This reverts commit baca8b24302dc02b00fcc2f8fee3e4173838d1a4.

In Scala~3, the rules for implicit ambiguities changed to take implicit parameters into account, thus introducing another, more direct, disambiguation mechanism.
All else being equal, an implicit definition that takes implicit parameters is considered less specific than an implicit definition does not take implicit parameters~\citep[Changes in Implicit Resolution]{odersky2013scala}.
As a result, implicit-based type-level programs written in Scala~3 do not need to use the patterns of ambiguities and priorities presented in this section (\ref{subsec:implicit-priorities} and \ref{subsec:implicit-ambiguities}).

>>>>

\begin{diff}
In Scala~3, the rules for implicit ambiguities changed to take implicit parameters into account, thus introducing another, more direct, disambiguation mechanism.
All else being equal, an implicit definition that takes implicit parameters is considered less specific than an implicit definition does not take implicit parameters~\citep[Changes in Implicit Resolution]{odersky2013scala}.
As a result, implicit-based type-level programs written in Scala~3 do not need to use the patterns of ambiguities and priorities presented in this section (\ref{subsec:implicit-priorities} and \ref{subsec:implicit-ambiguities}).
\end{diff}
